Evaluating infectious disease forecasts with allocation scoring rules

### 2023-12-04 alloscore_manuscript/alloscore-application.Rnw
First attempt at getting detailed AS info inside Rnw

Forecasts and allocations for a selection of states with high numbers of hospitalizations on January 3, 2022 reveal mechanics about how allocations are made (Figure \ref{fig:thermometer-plot}).
As described in the methods above, allocations for a given location from a specific model are generated by finding the single quantile of the probabilistic forecast across all locations that reaches the resource allocation limit (in this case, assumed to be 15,000).
A direct comparison between the forecasts from the JHUAPL-Bucky and CU-select models show that while the JHUAPL-Bucky forecast distributions were closer to the eventual observations in many states, the allocations suggested by those forecasts often were more inefficient than those from the CU-select model (Figure \ref{fig:thermometer-plot}).
For JHUAPL-Bucky, the allocations were assigned around the 25th quantile of the predictive distribution and for CU-select it was around the 90th percentile. \ngr{could we make these more specific?}
This reflects that in general the JHUAPL-Bucky forecasts assigned more probabilities to higher values and thus a low quantile value across all locations reached the allocation limit of 15,000.
In California, New York and Texas, the eventually observed number of hospital admissions was closer to the predicted median from JHUAPL-Bucky and was contained in JHUAPL-Bucky's 80\% PI. However for each of these three states, the resource allocation was lower and therefore resulted in more hypothetical unmet need than CU-select allocations.
In Florida, the forecast from JHUAPL-Bucky missed by a wide margin (as did the forecast from CU-select) and the allocation was nearly XX units lower than what was allocated according to the CU-select model. \ngr{add specific number here}

>>>>

Forecasts and allocations for a selection of states with high numbers of hospitalizations on January 3, 2022 reveal mechanics about how allocations are made (Figure \ref{fig:thermometer-plot}).
As described in the methods above, allocations for a given location from a specific model are generated by finding the single quantile of the probabilistic forecast across all locations that reaches the resource allocation limit (in this case, assumed to be 15,000).
A direct comparison between the forecasts from the JHUAPL-Bucky and CU-select models show that while the JHUAPL-Bucky forecast distributions were closer to the eventual observations in many states, the allocations suggested by those forecasts often were more inefficient than those from the CU-select model (Figure \ref{fig:thermometer-plot}).

<<detailedASinfo>>=
source("R/run-alloscore.R")
as_Buck <- run_alloscore(
  forecast_data = forecast_data, 
  truth_data = truth_data,
  one_reference_date = "2021-12-20",
  one_model = "JHUAPL-Bucky",
  one_K = 15000,
  slim = FALSE)

as_CU <- run_alloscore(
  forecast_data = forecast_data, 
  truth_data = truth_data,
  one_reference_date = "2021-12-20",
  one_model = "CU-select",
  one_K = 15000,
  slim = FALSE)

Buck_quantile <- round(1 - as_Buck$lam,2)*100
CU_quantile <- round(1 - as_CU$lam,2)*100

FL_allocs <- Kat15k_alloscores |> 
   dplyr::filter(
     model %in% c("JHUAPL-Bucky", "CU-select"), 
     reference_date == "2021-12-20", 
     abbreviation == "FL") |>
  dplyr::select(model, x) |>
  tibble::deframe()
FL_diff <- round(FL_allocs["CU-select"] - FL_allocs["JHUAPL-Bucky"])
@

For JHUAPL-Bucky, the allocations were assigned at the \Sexpr{Buck_quantile}th quantile of the predictive distribution and for CU-select it was at the \Sexpr{CU_quantile}th percentile. 
This reflects that in general the JHUAPL-Bucky forecasts assigned more probabilities to higher values and thus a low quantile value across all locations reached the allocation limit of 15,000.
In California, New York and Texas, the eventually observed number of hospital admissions was closer to the predicted median from JHUAPL-Bucky and was contained in JHUAPL-Bucky's 80\% PI. However for each of these three states, the resource allocation was lower and therefore resulted in more hypothetical unmet need than CU-select allocations.
In Florida, the forecast from JHUAPL-Bucky missed by a wide margin (as did the forecast from CU-select) and the allocation was \Sexpr{FL_diff} units lower than what was allocated according to the CU-select model.
